# openfda
## Convenient access to the OpenFDA API

This package provides some simple helpers for accessing the OpenFDA API
from R.  It uses the `jsonlite` and `magrittr` packages to provide a 
simple way to convert from OpenFDA queries to R dataframes suitable
for quick analysis and plotting.

## Installation

This library has not yet been added to CRAN, so you'll need the devtools
package to install it:

```R
install.packages("devtools")
````

Once devtools is installed, you can grab this package:

```R
library("devtools")
devtools::install_github("rjpower/openfda-R")
```

Load it in like any other package:

```{r}
library("openfda")
```

## Examples

```{r, echo=FALSE, results='hide'}
library("knitr")
opts_knit$set(upload.fun = imgur_upload, base.url = NULL)
```

```{r}
patient_ages = fda_query("/drug/event.json") %>%
               fda_count("patient.patientonsetage") %>%
               fda_exec()
               
# patient ages is now a data frame with "term" and "count" columns
# let's plot it with ggplot2
library("ggplot2")
qplot(x=term, y=count, data=patient_ages)
```

You can filter the results to count on using the `fda_filter()` method:

```{r}
paxil_ages = fda_query("/drug/event.json") %>%
               fda_filter("patient.drug.openfda.generic_name", "paroxetine")
               fda_count("patient.patientonsetage") %>%
               fda_exec()
```

Using this API with your API key is easy: just add
`fda_api_key("MY_KEY")` to your pipeline.

```{r}
patient_ages = fda_query("/drug/event.json") %>%
               fda_api_key("MYKEY") %>%
               fda_count("patient.patientonsetage") %>%
               fda_exec()
```

You can also specify options up front and re-use the query:

```{r}
age_query = fda_query("/drug/event.json") %>%
            fda_api_key("MYKEY") %>%
            fda_count("patient.patientonsetage");

paxil_ages = age_query %>% fda_filter("patient.drug.openfda.generic_name", "paroxetine") %>% fda_exec()
zoloft_ages = age_query %>% fda_filter("patient.drug.openfda.generic_name", "sertraline") %>% fda_exec()
```

R documentation for each method is also provided in the package (`? fda_exec`).
